---
title: "Stat20 0823"
output: html_document
---
##Introduction
* Prof. Stoyanov's Lectures: TuTh 9:30-11 AM, 2050 Valley Life Sciences Bldg
* GSI : Lei Zhang
* Email: lei_zhang@berkeley.edu
* Office Hour: 
* Books: Statistics (fourth edition) by Freedman, Pisani and Purves 
* Software: R and R Studio for statistical analysis 
* Homework: 
* Quiz: 15min quiz every week. No cheatsheet. 3 quizzes can be dropped.
* You are not getting graded on the attendance




##Download R and RStudio
###Mac Users
To Install R

1.  Open an internet browser and go to https://cran.cnr.berkeley.edu/.
2.  Click on the "Download R for (Mac) OS X" link at the top of the page.
3.  Click on the file containing the latest version of R
4.  Save the .pkg file, double-click it to open, and follow the installation instructions

Now that R is installed, you need to download and install RStudio.

To Install RStudio

1.  Go to www.rstudio.com and click on the "Download RStudio" button.
2.  Click on "Download RStudio Desktop."
3.  Click on the version recommended for your system, or the latest Mac version, save the .dmg file on your computer, double-click it to open, and then drag and drop it to your applications folder.


###Windows Users
To Install R:

1.  Open an internet browser and go to https://cran.cnr.berkeley.edu/.
2.  Click on the "Download R for Windows" link at the top of the page.
3.  Click on "install R for the first time."
4.  Click on "Download R 3.5.1 for Windows "
5.  Click "Download R for Windows" and save the executable file somewhere on your computer.  
6.  Run the .exe file and follow the installation instructions.  

Now that R is installed, you need to download and install RStudio. 

To Install RStudio,

1.  Go to www.rstudio.com and click on the "Download RStudio" button.
1.  Click on "Download RStudio Desktop."
3.  Click on the version recommended for your system, or the latest Windows version, and save the executable file.  
4.  Run the .exe file and follow the installation instructions.     


##Download ggplot2
```{r, eval = FALSE}
install.packages("ggplot2")
```

After you download ggplot2, remeber to load it. A few examples of ggplot2.

```{r}
library(ggplot2)

data("midwest", package = "ggplot2")#load the data
head(midwest)#return the first part of data
tail(midwest)#return the last part of data
```

```{r}
#simple scatter plot
ggplot(midwest, aes(x=area, y=poptotal)) +
  geom_point()
```

```{r}
#simple line plot
ggplot(midwest, aes(x=area, y=poptotal)) +
  geom_line()
```

```{r}
#scatter plot iwth title
ggplot(midwest, aes(x=area, y=poptotal)) +
  geom_point() +
  labs(title="Area Vs Population", subtitle="From midwest dataset", y="Population", x="Area", caption="Midwest Demographics")
```


##References
* https://courses.edx.org/courses/UTAustinX/UT.7.01x/3T2014/56c5437b88fa43cf828bff5371c6a924/
* http://r-statistics.co/Complete-Ggplot2-Tutorial-Part1-With-R-Code.html